sensi_an_rotations1. Start of sensitivity analysis for rotations.

### 2019-02-06 inst/documents/rotations_notes.Rmd
document

@@

@@

@@

For rotations send Jim a scaled down version of the rotations sensitivity analysis code. That just runs the sensitivity analysis and Jim will have a go at parallelising it.

Still occasionally getting error from shinyUI resistrot :
Warning: Error in raf_get: object 'RAF' not found

@@

~ ask Ian to check through the rotations algebra when he writes up the SI.

@@

Combining the high-dose/refuge strategy and self-limiting transgenic
insects in resistance management- a test in experimental mesocosms 
Zhou2017

>>>>

For rotations sent Jim a scaled down version of the rotations sensitivity analysis code. That just runs the sensitivity analysis and Jim will have a go at parallelising it.

@@

6/2/19

before meeting with Jim to look at rotations code

previous error in raf_get() seems OK now

@@

# todo: we want to look at changing insecticides according to mortality rather than resistance frequency

# Jim suggest

@@

@@

@@
